Fixed-Parameter Tractable Sampling for RNA Design with Multiple Target Structures

### 2018-09-21 supplement.tex

\begin{figure}
  \begin{center}
    {\sf \bfseries A}\includegraphicstop[width=0.45\textwidth]{Figs/Plots/PKB00211_PKB00239_0_GC_content}
    ~~~~~{\sf \bfseries B}
    \includegraphicstop[width=0.45\textwidth]{Figs/Plots/supp_3str_GC_content}
  \end{center}
  \caption{Distribution of the \GCb-content \GCb\% in the experiments of (A) Fig.~\ref{fig:energydist-pk} of the main text and (B) Suppl.~Fig.~\ref{fig:energydist}.}
  \label{fig:gc-content}
\end{figure}

>>>>

\begin{figure}
  \begin{center}
    {\sf \bfseries A}~\includegraphicstop[width=0.45\textwidth]{Figs/Plots/PKhttps://v2.overleaf.com/6339486874jnyvnycthtddB00211_PKB00239_0_GC_content}
    ~~~~~{\sf \bfseries B}~\includegraphicstop[width=0.45\textwidth]{Figs/Plots/supp_3str_GC_content}
  \end{center}
  \caption{Distribution of the \GCb-content \GCb\% in the experiments of (A) Fig.~\ref{fig:energydist-pk} of the main text and (B) Suppl.~Fig.~\ref{fig:energydist}.}
  \label{fig:gc-content}
\end{figure}
